Combining formal and distributional models of predicate semantics

### 2016-03-11 papers/acl2016/paper.tex
Added a figure to the intro, fixed some other stuff
Former-commit-id: 2a83901ecef50797aac82ce063aaa8e877194740

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{amsmath}
\usepackage{times}
\usepackage{latexsym}
\usepackage{color}

\newcommand{\secref}[1]{Section~\ref{sec:#1}}
\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
\newcommand{\algref}[1]{Algorithm~\ref{alg:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
\newcommand{\mattnote}[1]{\textcolor{red}{NOTE: #1}}
\newcommand{\blank}{\_\_\_}
\newcommand{\predicate}[1]{\ensuremath{\textsc{#1}}}
\newcommand{\entity}[1]{\ensuremath{\mathrm{#1}}}

@@

  In this paper, we present a method that incorporates logical statements
  derived from a knowledge base into distributional models of categories and
  relations.  Instead of mapping a phrase to a single logical statement, as
  done by semantic parsers, our method uses logical statements as features
  added to distributional models of words, allowing the model to learn that
  Freebase entities that are "honchos" are people, not buildings, and that they
  are frequently CEOs or film producers.  We use these models in an
  open-vocabulary semantic parsing task, showing a 63\% relative improvement in
  mean average precision over a distributional-only model, and a X\%
  improvement over a formal-only approach.

@@

How should a computer program represent the meaning of a word or a phrase?  The
answer to this question has a long and rich history.  Motivated by
Harris's distributional
hypothesis~\cite{harris-1954-distributional-hypothesis}, much work has been put
into representing words as collections of the contexts in which they appear.
Recent work with neural networks and word embeddings have shown that these
representations can be very useful for a number of natural language processing
tasks. \mattnote{cite something here}

At the same time, other researchers have found Montague's ideas about English
as a formal language to be useful~\cite{montague-1974-english-formal-language}.
Modern semantic parsers make use of a model-theoretic semantics that represents
words and phrases as formal predicates.  These predicates are then typically
mapped onto a query over a structured knowledge base, such as
Freebase~\cite{freebase-2008-bollacker}.  This kind of modeling allows semantic
parsers to handle the compositional structure of natural language and to
leverage large, curated knowledge sources to perform various natural language
processing tasks.  \mattnote{cite some semantic parsing papers}

Both of these approaches to modeling predicate semantics have aspects that are
very appealing.  It is relatively straightforward to learn a distributional
vector for every word or phrase in a corpus, allowing easy generalization from
words labeled with part of speech tags or dependency information to other words
that are distributionally similar.  Yet distributional approaches struggle to
make good use of the structured information contained in curated knowledge
sources like Freebase and WordNet~\cite{wordnet-1995}.  On the other hand,
because formal approaches to semantics typically model word meaning in terms of
a structured knowledge source, their applicability is limited to the set of
concepts represented in that knowledge source---a semantic parser trained with
Freebase cannot even represent words whose meaning has no correlate in the
Freebase ontology, such as ``front-runner'' and ``honcho''.

@@

To demonstrate these models, we focus on the task of fill-in-the-blank natural
language queries, such as ``Italian architect \blank{}''.  Similar to many
current semantic parsers, we first convert this natural language query into a
logical form: $\lambda x. \predicate{architect}(x) \land
\predicate{architect\_N/N}(\entity{Italian}, x)$.  A typical semantic
parser (e.g., that of Kwiatkowski et
al.~\shortcite{kwiatkowski-2013-ontology-matching}) would then try to map this
logical form to a Freebase query, matching \entity{Italian} to
(\predicate{/people/person/nationality}, \entity{Italy}) and
\predicate{architect} to (\predicate{/type/object/type},
\entity{/architecture/architect}).  In contrast, we follow Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} in learning a
model for each predicate that can give a \emph{score} to potential arguments.
However, while the models of Krishnamurthy and Mitchell are purely
distributional, using Freebase only as a means of finding entities in text, we
inject additional information from Freebase into the models for each predicate.
The model we learn for \predicate{architect} has a \emph{feature} capturing the
fact that an entity has the type \entity{/architecture/architect} in Freebase,
and the model for \predicate{architect\_N/N} has a \emph{feature} capturing
whether the first argument is the country of nationality of the second
argument.

This is a fundamentally new kind of predicate semantics.  It is
distributional---part of the model is still trained in a manner very similar to
word2vec---yet it is also formal.  However, instead of committing to a single
Freebase query to represent a phrase, as traditional formal approaches do, our
models are flexible, encoding many possible Freebase queries as features that
can give hints to the model.  Thus words that would be impossible to represent
as a single Freebase query can still benefit from the information contained in
Freebase---our model for ``front-runner'' learns that acceptable entities are
politicians, even though there is no exact encoding of ``front-runner'' in
Freebase.

The rest of this paper is organized as follows.  In \secref{background}, we
describe the relevant background necessary to understand the models we propose,
and we situate our model in the context of related work.  In \secref{method},
we give a formal description of our models of predicate semantics.  In
\secref{evaluation}, we present experimental results on fill-in-the-blank
natural language query task.  Using web text linked to Freebase as our training
and test data, we show a 63\% relative improvement over prior work, giving a
new state-of-the-art result on this dataset.  In \secref{discussion}, we give a
detailed discussion of the benefits and drawbacks of the models we have
proposed.  We then conclude in \secref{conclusion}.

@@

\mattnote{Add a figure here to demonstrate the logical forms.}

This system predicts a denotation $\gamma$, i.e., a set of Freebase
entities, for a natural language text $s$, using the following
probabilistic model:

\begin{align*}
P(\gamma | s) & = \sum_w \sum_\ell P(\gamma | \ell, w) P(w ; \theta, \phi) P(\ell | s)
\end{align*}

In this equation, $P(\ell | s)$ represents a semantic parser that
produces a logical form $\ell$ given the text $s$. This logical form
contains open-vocabulary predicates, as in the ``architect'' example
above. This factor is deterministic, meaning that it assigns
probability one to a single logical form. The second factor $P(w)$
represents a distribution over possible worlds $w$, where a world is
an assignment of truth values to all possible predicate
instances. This distribution can be efficiently represented using a
probabilistic database because each predicate instance is treated as
an independent random variable. The truth probabilities of these
variables are predicted using a matrix factorization approach similiar
to that of Riedel et al., \shortcite{riedel-2013-mf-universal-schema};
$\theta$ and $\phi$ represent the parameters of the matrix
factorization. Finally, $P(\gamma | \ell, w)$ represents the
deterministic evaluation of the logical form $\ell$ on the world $w$
to produce a denotation $\gamma$. This factor is similar to other
semantic parsing work, where it represents the deterministic
evaluation of a query against a given database. Algorithms from the
probabilistic databases community enable us to efficiently compute the
marginal probability that an entity $e$ is in the denotation of a
sentence, $\sum_\gamma P(e \in \gamma | s)$, for a large number of
queries; we refer the reader to (TODO).

The training problem in this model is to learn the parameters $\theta$
and $\phi$ of the probabilistic database. The probability of a
category instance $c(e)$ and relation instance $r(e_1, e_2)$ in the
database is given by:

\begin{align*}
  P(c(e) & = \true{}) & = & \sigma ( \theta_c^T \phi_e ) \\
  P(r(e_1, e_2) & = \true{}) & = & \sigma ( \theta_r^T \phi_{(e_1, e_2)} )
\end{align*}

The parameters $\theta$ represent $k$-dimensional embeddings of each
category and relation predicate, and the parameters $\phi$ represent
$k$-dimensional embeddings of each Freebase entity and entity
pair. The probability of a predicate instance is the inner product of
the corresponding predicate and entity embeddings. Thus, predicates
with nearby embeddings will have similar distributions over the
entities in their denotation.

The parameters $\theta$ and $\phi$ are learned from predicate/entity
co-occurrence counts collected from a large corpus. The training data
consists of query/entity pairs, $\{(\ell^i, e^i)\}$, where the entity
$e^i$ is observed to be an element of $\ell^i$'s denotation. These
pairs are collected by semantically parsing entity-linked sentences
and simplifying the resulting logical forms to identify conjunctions
of predicates where all arguments are bound to specific
entities. Extracting an entity from this conjunction results in a
query/entity pair. The model is trained using a ranking objective that
learns to rank the observed entities for each query above unobserved
entities.

@@

We compare three models in our experiments: a distributional-only model, a
formal-only model, and our proposed model, which is both distributional and
formal.  The distributional-only model is the model proposed by Krishnamurthy
and Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} and
described in \secref{jayant-semparse}.  The combined model is the model
described in \secref{sec:formal-and-distributional}, while the formal-only
model removes the distributional component from the combined model (i.e., all
parameters $\theta$ and $\phi$ from the distributional portion of the model are
fixed at zero during training and test).  Note that this formal-only baseline
is also new to this work---we are not aware of any other work that models
language in terms of features derived from a formal knowledge base.

@@

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|}
    \hline
    Method & MAP & MRR \\
    \hline
    Distributional-only & .239 & ?? \\
    Distributional-only (old lfs) & ?? & ?? \\
    \hline
    Formal-only & ?? & ?? \\
    Formal-only (old lfs) & ?? & ?? \\
    \hline
    Combined model & \textbf{.340} & ?? \\
    Combined model (old lfs) & ?? & ?? \\
    \hline
  \end{tabular}
  \caption{Results on the development set for our fill-in-the-blank task.  The
  combined model improves MAP by 42\% compared to the distributional-only
  baseline.  Additionally, the improved logical forms presented in
  \secref{better-lfs} significantly improve all models.}
  \label{tab:dev-results}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|}
    \hline
    Method & MAP & MRR \\
    \hline
    Distributional-only & .231 & ?? \\
    \ \ \ -related entities & .170 & ?? \\
    \hline
    Formal-only & ?? & ?? \\
    \hline
    Combined model & \textbf{.376} & ?? \\
    \hline
  \end{tabular}
  \caption{Results on the final test set for our fill-in-the-blank task.  The
  combined model improves MAP by 63\% relative to the distributional-only
  baseline.  Additionally, allowing the distributional-only model to use
  Freebase to propose candidates improves MAP by 6 points absolute due to
  improved recall.}
  \label{tab:final-results}
\end{table}

\tabref{final-results} shows that these improvements are consistent on the
final test set, as well.  The performance improvement seen by the combined
model is actually larger on this set, going from a MAP of .231 to .376, a 63\%
relative improvement.  In this table, we also show the improvement gained by
allowing the distributional-only model to propose candidate entities that are
related in Freebase (see \secref{better-candidates}).  Even though these
candidates are always ranked at the bottom of the list of predictions (with a
score of 0), the additional recall provided by being able to propose more
entities raises MAP of the distributional-only model from .170 to .231.

>>>>

\documentclass[11pt]{article}
\usepackage{acl2016}
\usepackage{amsmath}
\usepackage{times}
\usepackage{latexsym}
\usepackage{color}
\usepackage{booktabs}
\usepackage{subfig}

\newcommand{\secref}[1]{Section~\ref{sec:#1}}
\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
\newcommand{\algref}[1]{Algorithm~\ref{alg:#1}}
\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
\newcommand{\mattnote}[1]{\textcolor{red}{NOTE: #1}}
\newcommand{\blank}{\underline{\hspace{.5cm}}}
\newcommand{\predicate}[1]{\ensuremath{\textsc{#1}}}
\newcommand{\entity}[1]{\ensuremath{\textsc{#1}}}

@@

  In this paper, we present a method that incorporates logical statements
  derived from a knowledge base into distributional models of categories and
  relations.  Instead of mapping a phrase to a single logical statement, as
  done by semantic parsers, our method uses logical statements as features
  added to distributional models of words, allowing the model to learn that
  Freebase entities that are "honchos" are people, not buildings, and that they
  are frequently CEOs or film producers.  We use these models in an
  open-vocabulary semantic parsing task, showing a 62\% relative improvement in
  mean average precision over a distributional-only model.

@@

How should a computer program represent the meaning of a word or a phrase?  The
answer to this question has a long and rich history.  Motivated by Harris's
distributional hypothesis~\cite{harris-1954-distributional-hypothesis}, much
work has been put into representing words as collections of the contexts in
which they appear.  Recent work with neural networks and word embeddings have
shown that these representations can be very useful for a number of natural
language processing tasks (see, e.g., the work Mikolov et
al.~\shortcite{mikolov-2013-word2vec} and papers that cite them).  This
approach to modeling semantics is appealing because word embeddings can be
trained on unlabeled text, allowing for very broad coverage, although shallow,
semantics.

\begin{figure*}[ht]
  \small
  \begin{minipage}{0.28\linewidth}
    \textbf{Input Text}\\Italian architect Andrea Palladio
  \end{minipage}
%
  ~~ $\rightarrow$ ~~~~~~
%
  \begin{minipage}{0.7\linewidth}
    \textbf{Logical Form}\\
    $\predicate{architect}(\entity{Palladio})~\land~\predicate{architect\_N/N}(\entity{Italy}, \entity{Palladio})$
  \end{minipage}

  \vspace{.1in}
  \begin{minipage}{0.5\linewidth}
    \textbf{Category models}\\
    \begin{tabular}{@{}lll}
      \predicate{architect}: & $\theta$: &[.2, -.6, \ldots] \\
      & $\omega$: & \textsc{type:architect} $\rightarrow$ .52 \\
      &           & \textsc{type:designer} $\rightarrow$ .32 \\
      &           & \textsc{nationality:Italy} $\rightarrow$ .20 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}
  \begin{minipage}{0.5\linewidth}
    \textbf{Relation models}\\
    \begin{tabular}{@{}lll}
      \predicate{architect\_N/N}: & $\theta$: &[-.9, .1, \ldots] \\
      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ .29 \\
      &           & \textsc{/structure/architect} $\rightarrow$ .11 \\
      &           & \textsc{/person/ethnicity\textsuperscript{-1}} $\rightarrow$ .05 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}

  \vspace{.1in}
  \begin{minipage}{0.5\linewidth}
    \textbf{Entity models}\\
    \begin{tabular}{@{}lll}
      \predicate{Palladio}: & $\phi$: &[.15, -.8, \ldots] \\
      & $\psi$: & \textsc{type:architect} $\rightarrow$ 1 \\
      &           & \textsc{type:designer} $\rightarrow$ 0 \\
      &           & \textsc{nationality:Italy} $\rightarrow$ 1 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}
  \begin{minipage}{0.5\linewidth}
    \textbf{Entity pair models}\\
    \begin{tabular}{@{}lll}
      \predicate{(Italy, Palladio)}: & $\phi$: &[-.8, .2, \ldots] \\
      & $\omega$: & \textsc{/person/nationality\textsuperscript{-1}} $\rightarrow$ 1 \\
      &           & \textsc{/structure/architect} $\rightarrow$ 0 \\
      &           & \textsc{/person/ethnicity\textsuperscript{-1}} $\rightarrow$ 0 \\
      &           & $\cdots$
    \end{tabular}
  \end{minipage}

  \vspace{-.1in}
  \caption{Overview of the components of our model.  Given an input text, we
  use a CCG parser and an entity linker to produce a logical form that is a
  conjunction of predicates involving the entities in the text.  For each
  predicate (both categories and relations), we learn a distributional vector
  $\theta$, as well as weights $\omega$ associated with formal features from
  Freebase (which are shortened to fit in the figure).  For each entity and
  entity pair, we also learn a distributional vector $\phi$, and we extract a
  feature vector $\psi$ from Freebase.  These models are combined to assign a
  probability to the input text, assigning a high probability to the above
  text, and a low probability to ``Italian architect Barack Obama''.}
  \label{fig:overview}
  \vspace{-.1in}
\end{figure*}

At the same time, other researchers have found Montague's ideas about English
as a formal language to be useful~\cite{montague-1974-english-formal-language}.
Modern semantic parsers make use of a model-theoretic semantics that represents
words and phrases as formal predicates.  These predicates are then typically
mapped onto a query over a structured knowledge base, such as
Freebase~\cite{freebase-2008-bollacker}.  This kind of modeling allows semantic
parsers to handle the compositional structure of natural language and to
leverage large, curated knowledge sources to perform various natural language
processing
tasks~\cite{zettlemoyer-2005-ccg,kwiatkowski-2013-ontology-matching,berant-2013-semantic-parsing-qa}.  However,
semantic parsers are fundamentally limited by the schema of the ontology they
are trained on---a semantic parser trained with Freebase cannot even represent
words whose meaning has no correlate in the Freebase ontology, such as
``front-runner'' and ``honcho''.

@@

To demonstrate these models, we focus on the task of fill-in-the-blank natural
language queries, such as ``Italian architect \blank{}''.  Similar to many
current semantic parsers, we first convert this natural language query into a
logical form: $\lambda x. \predicate{architect}(x) \land
\predicate{architect\_N/N}(\entity{Italy},
x)$.\footnote{\predicate{architect\_N/N} represents a noun-compound
relationship between two entities mediated by the word ``architect'', as in
``Italian architect Andrea Palladio''.  This is in contrast to, e.g.,
\predicate{'s\_architect} or \predicate{architect\_of}, both of which also are
mediated by ``architect'', but through different syntax.  N/N is how
CCG~\cite{steedman-2006-ccg} represents a noun compound.} A typical semantic
parser (e.g., that of Kwiatkowski et
al.~\shortcite{kwiatkowski-2013-ontology-matching}) would then try to map this
logical form to a single Freebase query, likely involving
(\predicate{/people/person/nationality}: \entity{Italy}) and
(\predicate{/type/object/type}: \entity{/architecture/architect}).  Instead of
restricting ourselves to modeling only what can be represented as a Freebase
query, we follow Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} in learning a
model for each predicate that can give a \emph{score} to potential arguments.
The model for \predicate{architect}, e.g., should give high scores to
\entity{Andrea Palladio} and \entity{Frank Lloyd Wright}, and low scores to
\entity{Italy}, \entity{BarackObama}, etc.  However, while the models of
Krishnamurthy and Mitchell are purely distributional, using Freebase only as a
means of finding entities in text, we inject additional information from
Freebase into the models for each predicate.  The model we learn for
\predicate{architect} has a \emph{feature} capturing the fact that an entity
has the type \entity{/architecture/architect} in Freebase, and the model for
\predicate{architect\_N/N} has a \emph{feature} capturing whether the first
argument is the country of nationality of the second argument.  An overview of
the components of our model is given in \figref{overview}.

This is a new kind of predicate semantics.  It is distributional---part of the
model is still trained in a manner very similar to word2vec---yet it is also
formal.  However, instead of committing to a single Freebase query to represent
a phrase, as traditional formal approaches do, our models are flexible,
encoding many possible Freebase queries as features that can give hints to the
model.  Thus words that would be impossible to represent as a single Freebase
query can still benefit from the information contained in Freebase---our model
for ``front-runner'' learns that acceptable entities are politicians, even
though there is no exact encoding of ``front-runner'' in Freebase.

The rest of this paper is organized as follows.  In \secref{background}, we
describe the relevant background necessary to understand the models we propose,
and we situate our model in the context of related work.  In \secref{method},
we give a formal description of our models of predicate semantics.  In
\secref{evaluation}, we present experimental results on fill-in-the-blank
natural language query task.  Using web text linked to Freebase as our training
and test data, we show a 62\% relative improvement over prior work, giving a
new state-of-the-art result on this dataset.  In \secref{discussion}, we give a
detailed discussion of the benefits and drawbacks of the models we have
proposed.  We then conclude in \secref{conclusion}.

@@

Krishnamurthy and
Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} introduced a
technique for learning semantic parsers with open predicate vocabularies.
Instead of mapping text to Freebase queries, they applied the matrix
factorization semantics used by Riedel et
al.~\shortcite{riedel-2013-mf-universal-schema} in knowledge base completion to
the task of learning predicate semantics in a semantic parser.  This method
assigns truth values to instantiated predicates like
\predicate{architect}(\entity{AndreaPalladio}) in a probabilistic database.
The models Krishnamurthy and Mitchell use for the predicates and entities are
essentially equivalent to modern techniques for constructing word embeddings,
implicitly factorizing a cooccurrence matrix between categories and entities,
and relations and entity pairs~\cite{levy-2014-w2v-as-mf}.  This implicit
factorization has two sets of parameters: each predicate (category or relation)
has a learned $k$-dimensional embedding $\theta$, and each entity and entity
pair has a learned embedding $\phi$.  The probability assigned to a category
instance $c(e)$ and relation instance $r(e_1, e_2)$ in the probabilistic
database is given by:

\begin{align*}
  P(c(e) = \true{}) &= \sigma ( \theta_c^T \phi_e ) \\
  P(r(e_1, e_2) = \true{}) &= \sigma ( \theta_r^T \phi_{(e_1, e_2)} )
\end{align*}

The probability of a predicate instance is the (sigmoided) inner product of the
corresponding predicate and entity embeddings. Thus, predicates with nearby
embeddings will have similar distributions over the entities in their
denotation.  The model is trained using a ranking objective that learns to rank
the observed entities for each query above unobserved entities.  The
probabilistic database produced by these predicate models is then input to a
reasoning system that can handle a subset of first-order logic.

In this paper, we use the system produced by Krishnamurthy and Mitchell,
changing only the models of predicate semantics, as described in
\secref{method}.

@@

We compare three models in our experiments: a distributional-only model, a
formal-only model, and our proposed model, which is both distributional and
formal.  The distributional-only model is the model proposed by Krishnamurthy
and Mitchell~\shortcite{krishnamurthy-2015-semparse-open-vocabulary} and
described in \secref{jayant-semparse}.  The combined model is the model
described in \secref{formal-and-distributional}, while the formal-only
model removes the distributional component from the combined model (i.e., all
parameters $\theta$ and $\phi$ from the distributional portion of the model are
fixed at zero during training and test).  Note that this formal-only baseline
is also new to this work---we are not aware of any other work that models
language in terms of features derived from a formal knowledge base.

@@

\begin{table}
  \centering
  {\small
    \begin{tabular}{lccc}
      \toprule
      Method & MAP & Weighted MAP & MRR \\
      \midrule
      Distributional-only & .284 & .371 & .379 \\
      \ \ \ (old lfs) & ?? & ?? & ?? \\
      \midrule
      Formal-only & .276 & .469 & .334 \\
      \ \ \ (old lfs) & ?? & ?? & ?? \\
      \midrule
      Combined model & \textbf{.335} & \textbf{.477} & \textbf{.429} \\
      \ \ \ (old lfs) & ?? & ?? & ?? \\
      \bottomrule
    \end{tabular}
  }
  \caption{Results on the development set for our fill-in-the-blank task.  The
  combined model improves MAP by 42\% compared to the distributional-only
  baseline.  Additionally, the improved logical forms presented in
  \secref{better-lfs} significantly improve all models.}
  \label{tab:dev-results}
\end{table}

@@

\begin{table}
  \centering
  {\small
    \begin{tabular}{lccc}
      \toprule
      Method & MAP & Weighted MAP & MRR \\
      \midrule
      Distributional-only & .229 & .275 & .312 \\
      \ \ \ -related entities & .163 & .163 & .288 \\
      \midrule
      Formal-only & .355 & .495 & .419 \\
      \midrule
      Combined model & \textbf{.370} & \textbf{.513} & \textbf{.469} \\
      \bottomrule
    \end{tabular}
  }
  \caption{Results on the final test set for our fill-in-the-blank task.  The
  combined model improves MAP by 62\% relative to the distributional-only
  baseline.  Additionally, allowing the distributional-only model to use
  Freebase to propose candidates improves MAP by 6.6 points absolute due to
  improved recall.}
  \label{tab:final-results}
\end{table}

\tabref{final-results} shows that these improvements are consistent on the
final test set, as well.  The performance improvement seen by the combined
model is actually larger on this set, going from a MAP of .229 to .370, a 62\%
relative improvement.  In this table, we also show the improvement gained by
allowing the distributional-only model to propose candidate entities that are
related in Freebase (see \secref{better-candidates}).  Even though these
candidates are always ranked at the bottom of the list of predictions (with a
score of 0), the additional recall provided by being able to propose more
entities raises MAP of the distributional-only model from .163 to .229.
